Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

This section supplies the proofs postponed from Section~\ref{sec:hv:type2}. The order of the proofs here will not strictly follow the sequence in which they are referenced in Section~\ref{sec:hv:type2}. In particular, we will prove Lemma~\ref{lmm:hv:type2:recur-output} before Lemma~\ref{lmm:hv:type2:properties}, because the claims of the former lemma can be used to construct a simple argument for the latter.

>>>>

This section supplies the proofs postponed from Section~\ref{sec:hv:type2}. The order of the proofs here will not strictly follow the sequence in which they are referenced in Section~\ref{sec:hv:type2}. In particular, we will prove Lemma~\ref{lmm:hv:type2:properties} before Lemma~\ref{lmm:hv:type2:recur-output}, because the claims of the former lemma can be used to construct a simple argument for the latter.
